## Wheeler-Smith (Bamberger-Vanecek)\index{Wheeler-Smith!variations!Bamberger-Vanecek (German)} {#sec-wheeler-smith-bamberger-vanecek}

Wheeler-Smith (Bamberger-Vanecek) [-@{bamberger-vanecek}77, 186] is a German variation of [Wheeler-Smith](#sec-wheeler-smith) designed for both primary and secondary-age reading material. It calculates the grade level of a document based on [unit](#sec-glossary)\index{sentences!units} length and number of complex words.

::: {.callout-note icon=false}
## Wheeler-Smith (Bamberger-Vanecek) formula

$$
I = ((W/U)*((C/W)*100)) / 10
$$
:::

Where:

```{r, echo=F}
wheelersmithBVData <- tibble(col1 = c("I", "C", "W", "U"),
                             col2 = markdown_to_kable_cell(c("Index value",
                                      "Number of 3+ syllable^a^ words",
                                      "Number of words",
                                      "Number of units")))

colnames(wheelersmithBVData) <- rep('', ncol(wheelersmithBVData))
kableExtra::kbl(wheelersmithBVData, booktabs=T, centering=T, align='l', escape=F) %>%
  kableExtra::kable_classic(full_width=F) %>%
  footnote(alphabet = c(markdown_to_kable_footnote('“*drei- und mehrsilbigen*”')),
           escape=F, threeparttable=T)
```

Then, find the index value in the following chart to acquire the final readability score:

```{r, echo=F}
kableExtra::kbl(read_delim("data/WheelerSmithBV.txt", "\t", escape_double=F, trim_ws=T),
                booktabs=T, centering=T, linesep="",
                caption="Wheeler-Smith (Bamberger-Vanecek) Conversion Table",
                align='lr', escape=F)
```

::: {.notesection data-latex=""}
Although Bamberger and Vanecek [-@{bamberger-vanecek}77, 186] do not specify using units\index{sentences!units} instead of sentences, the use of units is assumed to match Wheeler-Smith [-@{wheeler-smith}398].

Based on the examples from Bamberger and Vanecek [-@{bamberger-vanecek}77, 186], index values should be truncated to one-point precision, not rounded.
:::
